---
title: "Machine Learning Course Project"
author: "Hubert LEVIEL"
date: "November 18th, 2015"
output: html_document
---

# Summary
The goal of this project is to build a machine learning algorithm to predict activity quality from activity monitors

# Loading and parting the data

We load the data, then immediately part it into training and testing
```{r, echo=TRUE}
data <- read.csv(url('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv'))
testing_set <- read.csv(url('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv'))

library(caret)
set.seed(555)
trainingIndex <- createDataPartition(data$classe, p=0.7, list=FALSE)
training <- data[trainingIndex,]
testing <- data[-trainingIndex,]
```

# Preprocessing
The summary of training data shows many NAs or unset values, so I choose to remove the columns with to many NAs or unset values.
Also we can see that some variables like X or window or date are ordered and shouldn't be used to build a model, neither the username. So I also remove the first 7 columns.
And then I remove the exact same columns from the testing.
```{r, echo=TRUE}
training.complete <- training[, colSums(is.na(training) | training=='' ) < nrow(training) * 0.5]
training.complete <- training.complete[, -c(1:7)]
testing.complete <- testing[,names(training.complete)]
testing_set.complete <- testing_set[,names(training.complete)[names(training.complete)!="classe"]]
dim(training.complete)
```

This leaves us with 53 columns (out of 160)
# Training
To predict the classe outcome, I am going to use Linear Discriminant Analysis (LDA) method of caret package, and train on other variables.

```{r, echo=TRUE}
mymod <- train(classe~., data=training.complete, method='qda', show=FALSE)
```

We can see that there is 90% accuracy with the training data
```{r, echo=TRUE}
table(predict(mymod, training.complete),training.complete$classe)
1-sum(predict(mymod, training.complete)!=training.complete$classe)/dim(training.complete)[1]
```

We can see that there is 90% accuracy with the test data
```{r, echo=TRUE}
table(predict(mymod, testing.complete),testing.complete$classe)
1-sum(predict(mymod, testing.complete)!=testing.complete$classe)/dim(testing.complete)[1]
```


```{r, echo=FALSE}

answers = predict(mymod, testing_set.complete)

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(as.character( answers))

```

